Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-18 paper/paper.tex
moving text
pass on intro

Differential testing~\cite{Brumley-etal-ss07} (DT) is a popular
approach that has been applied in a variety of contexts to find
functional bugs in
software~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior.
%% WHAT WE DID
This paper reports the results of a study we conducted to (i) assess
the reliability of existing JS engines and to (ii) evaluate the
importance of different factors when using DT for bug finding. More
precisely, we analyzed the impact of two orthogonal factors in the use
of DT: test mining and fuzzing. The first dimension, test mining,
considers the effect that \js{} test files mined from the repository
of a given open-source engine have in detecting functional bugs in
other engines. The second dimension, fuzzing, considers the impact of
fuzzing the mined files in bug detection.
%% WHAT WE FOUND
To sum, we found that \Fix{...}

@@

@@

\subsection{Expected Inconsistencies}

>>>>

Differential testing~\cite{Brumley-etal-ss07} (DT) is a popular
approach that has been applied in a variety of contexts to find
functional bugs in
software~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior. For example, Mozilla
runs JS files--created with the grammar-based fuzzer
jsfunfuzz~\cite{jsfunfuzz}--against different configurations of their
SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
across configurations. They use this technique since 2002 and have
been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, some of which are security bugs.
Cross-engine differential testing checks correctness by comparing the
output produced by \emph{different} engines on a given
input~\cite{patra2016learning}. The availability on the web of public
implementations of JS engines (see Table~\ref{tab:engines}) and test
suites makes this bug-finding approach very appealing.

%% WHAT WE DID
This paper reports the results of a study we conducted to (i) assess
the reliability of existing JS engines and to (ii) evaluate the
importance of different factors when using DT for bug finding. More
precisely, we analyzed the impact of two orthogonal factors in the use
of DT: test mining and fuzzing. The first dimension, test mining,
considers the effect that \js{} test files mined from the repository
of a given open-source engine have in detecting functional bugs in
other engines. The second dimension, fuzzing, considers the impact of
fuzzing the mined files in bug detection.
%% WHAT WE FOUND
To sum, we found that \Fix{...}

@@

\subsection{Randomness and Undefined Behavior}

@@
